### 2025-05-17 manuscripts/10-JERP-v3/manuscript_title_etc.tex
some edits

Do individuals with Hispanic surnames face labor market discrimination? This study analyzes the impact of Hispanic-sounding surnames on wages among inter-ethnic Americans with one White and one Hispanic parent. I find that individuals that likely have Hispanic surnames (i.e., those with a Hispanic father) often earn less, with a notable wage gap favoring those with White-sounding surnames. People born to Hispanic fathers and White mothers receive 0.2 fewer years of education than men born to White fathers and Hispanic mothers. Men born to Hispanic fathers and White mothers are 1 percentage point more likely to be unemployed, and they earn 5 percentage points less than those born to White fathers and Hispanic mothers. I also show that this gap can largely be explained by educational differences.  \PAPERJEL}

>>>>

Do individuals with Hispanic surnames face labor market discrimination? This study analyzes the impact of likely Hispanic surnames on wages among Americans with one White and one Hispanic parent. I find that individuals that likely have Hispanic surnames (i.e., those with a Hispanic father) often earn less, with a notable wage gap favoring those with White-sounding surnames. People born to Hispanic fathers and White mothers receive 0.2 fewer years of education than those born to White fathers and Hispanic mothers. Men born to Hispanic fathers and White mothers are 1 percentage point more likely to be unemployed, and they earn 5 percentage points less than those born to White fathers and Hispanic mothers. I also show that this gap can largely be explained by educational differences.  \PAPERJEL}
